An Open and Continuously Updated Fern Tree of Life (FTOL)

### 2022-04-01 ms/manuscript.Rmd
Use 'my' for timescale, convert workflow to tiff with pdftools

```{r workflow-save, eval = params$doc_type == "doc" }
# Copy workflow image if rendering to doc
fs::file_copy(
  here::here("images/workflow.tiff"),
  result_file(figure("workflow"), "tiff"),
  overwrite = TRUE)
```

@@

a <- ggtree(
  sanger_con_tree_dated, 
    layout = "fan", right = FALSE, size = 0.1, open.angle = 2) + 
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Eq", "Op", "Ma", "Os", "Gl")], 10) +
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Hy", "Sc", "Sal")], 14) +
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Cy", "Sac", "Li")], 17) +
  ftol_geom_cladelab("De", 36) +
  ftol_geom_cladelab("Pt", 26) +
  ftol_geom_cladelab("As", 34) +
  ftol_geom_cladelab("Po", 17) +
  scale_color_manual(values = clade_cols) +
  geom_treescale(
    width = 100, # 100 Ma
    fontsize = 2, 
    y = 5600, # Just above "top" of tree
    label = "100 Ma", 
    offset = 1000, # hack to get default scale width (lacks units) to go away
    offset.label = -10) +
  theme(legend.position = "none")

>>>>

```{r workflow-save, eval = params$doc_type == "doc" }
# Convert workflow image to tiff for submission
pdftools::pdf_convert(
  pdf = here::here("images/workflow.pdf"),
  filenames = result_file(figure("workflow"), "tiff"),
  format = "tiff",
  dpi = 300)
```

@@

a <- ggtree(
  sanger_con_tree_dated, 
    layout = "fan", right = FALSE, size = 0.1, open.angle = 2) + 
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Eq", "Op", "Ma", "Os", "Gl")], 10) +
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Hy", "Sc", "Sal")], 14) +
  ftol_geom_cladelab(
    clade_tibble$code[clade_tibble$code %in% c("Cy", "Sac", "Li")], 17) +
  ftol_geom_cladelab("De", 36) +
  ftol_geom_cladelab("Pt", 26) +
  ftol_geom_cladelab("As", 34) +
  ftol_geom_cladelab("Po", 17) +
  scale_color_manual(values = clade_cols) +
  geom_treescale(
    width = 100, # 100 Ma
    fontsize = 2, 
    y = 5600, # Just above "top" of tree
    label = "100 my", 
    offset = 1000, # hack to get default scale width (lacks units) to go away
    offset.label = -10) +
  theme(legend.position = "none")
